Do larger catchments respond different to forest cover change? Re-analysing a global data set.

### 2021-11-23 paper/Forest_and_Water/Forest_and_Water.tex
further paper updates and data correction

  \title{Do larger catchments respond different to forest cover change?
Re-analysing a global data set.}
    \author[The University of Sydney, INIA]{R. Willem Vervoort\corref{1}}
   \ead{willem.vervoort@sydney.edu.au} 
    \author[INIA]{Eliana Nervi}
   \ead{eliananervi@gmail.com} 
    \author[IMFIA]{Jimena Alonso\corref{2}}
   \ead{jalonso@fing.edu.uy} 
      \address[The University of Sydney]{School of Life and Environmental Sciences, The University of Sydney,
Sydney, NSW 2006, Australia}
    \address[INIA]{INIA, Uruguay}
    \address[IMFIA]{Institute of Fluid Mechanics and Environmental Engineering, School of
Engineering, Universidad de la República, 11200 Montevideo, Departamento
de Montevideo, Uruguay}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

Several additional data points from watershed studies were extracted
from Zhang et al. (2011), Zhao et al. (2010), Borg et al. (1988),
Thornton et al. (2007), Zhou et al. (2010), Rodriguez et al. (2010),
Ruprecht et al. (1991) and Peña-Arancibia et al. (2012), and these were
checked against the existing studies to prevent overlap. In the citation
column in the data set, in general the main reference for the calculated
change in streamflow was used, because sometimes the original study did
not provide the quantification of the change in streamflow (i.e.~Table 6
in Zhang et al. (2011))

@@

\begin{verbatim}
## 
## -- Column specification --------------------------------------------------------
## cols(
##   Watershed = col_double(),
##   Latitiude = col_double(),
##   Longitude = col_double(),
##   rvalue_1 = col_double()
## )
\end{verbatim}

\begin{verbatim}
## 
## -- Column specification --------------------------------------------------------
## cols(
##   site_name = col_double(),
##   lat = col_double(),
##   long = col_double(),
##   `Area(km2)` = col_double(),
##   `Forest typ` = col_character(),
##   C = col_character(),
##   rvalue_1 = col_double()
## )
\end{verbatim}

\begin{verbatim}
## Warning: Removed 7 rows containing missing values (position_stack).
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-3-1.pdf}

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-4-1.pdf}

@@

In this model, no direct interactions are assumed. The changes in forest
cover contain both positive (forestation) and negative values
(deforestation). In Zhang et al. (2017), these changes were jointly
analysed, assuming the effect on the change in flow was linear and
non-hysteretic. However, the impact of an increase in forest cover can
be different from the same fractional decrease in forest cover.
Therefore all the change in forest cover data is converted to positive
values, and an additional column (\emph{sign\_\{forest cover\}}) is
added that indicates whether it was a forest cover increase or decrease.
A further assumption in the model is that all continuous variables
\(Z_i\) (such as annual precipitation (Pa)) can have a linear or
non-linear relationship with \(\Delta Q \%\). This means that a smooth
function \(s()\) is applied to the \(Z_i\) variables.

@@

The overall dataset contains 312 observations of changes in flow. The
overall distribution of changes in flow is highly skewed as is the
distribution of changes in forest cover and Area. The values of changes
in flow greater than 100\% and smaller than -100\% clearly create long
tails on the change in flow distribution. Note also the large number of
studies with 100\% forest cover reduction.

\begin{verbatim}
## Warning: Removed 7 rows containing non-finite values (stat_bin).
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-8-1.pdf}

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-9-1.pdf}

This immediately shows that for the data related to forest decreases,
there is almost always a positive flow change. In other words, flow
almost always increased. However, for increases in forest cover, this is
not the case, and flow can both increase and decrease. However in both
cases the variability in the reported change in flow increases with the
increase in forest cover change.

@@

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign
## 
## Parametric coefficients:
##                     Estimate Std. Error t value Pr(>|t|)    
## (Intercept)           8.8466     6.5008   1.361    0.175    
## DeltaF_perc_pos       0.5364     0.1017   5.274 2.52e-07 ***
## Forest_Signincrease -32.4760     6.9367  -4.682 4.26e-06 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## 
## R-sq.(adj) =   0.16   Deviance explained = 16.6%
## GCV = 3278.3  Scale est. = 3246.8    n = 312
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model1-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Model required no smoothing parameter selectionModel rank =  3 / 3
\end{verbatim}

\begin{longtable}[]{@{}ccc@{}}
\toprule
\begin{minipage}[b]{0.11\columnwidth}\centering
Length\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\centering
Class\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\centering
Mode\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.11\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\centering
NULL\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\centering
NULL\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + Area_km2 + Pa_mm
## 
## Parametric coefficients:
##                       Estimate Std. Error t value Pr(>|t|)    
## (Intercept)          2.323e+01  9.189e+00   2.528   0.0120 *  
## DeltaF_perc_pos      5.424e-01  1.030e-01   5.265 2.64e-07 ***
## Forest_Signincrease -3.324e+01  6.955e+00  -4.779 2.73e-06 ***
## Area_km2            -1.867e-06  1.322e-05  -0.141   0.8878    
## Pa_mm               -1.067e-02  4.944e-03  -2.158   0.0317 *  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## 
## R-sq.(adj) =  0.168   Deviance explained = 17.9%
## GCV = 3269.3  Scale est. = 3217      n = 312
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model2-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Model required no smoothing parameter selectionModel rank =  5 / 5
\end{verbatim}

\begin{longtable}[]{@{}ccccc@{}}
\toprule
\begin{minipage}[b]{0.30\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
23.23\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
9.189\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
2.528\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
0.01197\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
0.5424\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
0.103\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
5.265\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
2.64e-07\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-33.24\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
6.955\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-4.779\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
2.733e-06\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{Area\_km2}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-1.867e-06\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
1.322e-05\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-0.1412\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
0.8878\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{Pa\_mm}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-0.01067\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
0.004944\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-2.158\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
0.03169\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + Area_km2 + Pa_mm + 
##     Latitude + Longitude
## 
## Parametric coefficients:
##                       Estimate Std. Error t value Pr(>|t|)    
## (Intercept)          3.504e+01  1.026e+01   3.415 0.000724 ***
## DeltaF_perc_pos      5.147e-01  1.027e-01   5.014 9.07e-07 ***
## Forest_Signincrease -3.793e+01  7.230e+00  -5.247 2.90e-07 ***
## Area_km2            -6.282e-06  1.327e-05  -0.474 0.636137    
## Pa_mm               -1.304e-02  5.055e-03  -2.580 0.010339 *  
## Latitude            -3.119e-01  1.255e-01  -2.484 0.013520 *  
## Longitude           -1.058e-02  3.965e-02  -0.267 0.789747    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## 
## R-sq.(adj) =  0.183   Deviance explained = 19.9%
## GCV = 3230.5  Scale est. = 3158      n = 312
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model3-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Model required no smoothing parameter selectionModel rank =  7 / 7
\end{verbatim}

\begin{longtable}[]{@{}ccccc@{}}
\toprule
\begin{minipage}[b]{0.30\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
35.04\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
10.26\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
3.415\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
0.0007243\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
0.5147\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
0.1027\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
5.014\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
9.071e-07\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-37.93\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
7.23\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-5.247\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
2.898e-07\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{Area\_km2}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-6.282e-06\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
1.327e-05\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-0.4736\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
0.6361\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{Pa\_mm}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-0.01304\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
0.005055\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-2.58\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
0.01034\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{Latitude}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-0.3119\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
0.1255\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-2.484\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
0.01352\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{Longitude}\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-0.01058\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
0.03965\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-0.2669\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
0.7897\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

The previous analysis suggests an influence of radiation on
evapotranspiration, and most likely related to the dryness index, as
also indicated in Zhang et al. (2017). Increased evapotranspiration
could lead to drier catchments, unless balanced by rainfall (such as
possibly in the tropics). This model introduces the dryness index as a
linear variable and drops the annual average precipitation as a
variables.

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + Area_km2 + Latitude + 
##     Longitude + Dryness
## 
## Parametric coefficients:
##                       Estimate Std. Error t value Pr(>|t|)    
## (Intercept)          6.031e-01  8.582e+00   0.070 0.944022    
## DeltaF_perc_pos      5.006e-01  1.036e-01   4.831 2.18e-06 ***
## Forest_Signincrease -3.898e+01  7.253e+00  -5.375 1.55e-07 ***
## Area_km2            -7.227e-06  1.317e-05  -0.549 0.583604    
## Latitude            -3.121e-01  1.249e-01  -2.500 0.012974 *  
## Longitude           -6.775e-03  3.958e-02  -0.171 0.864199    
## Dryness              1.370e+01  3.628e+00   3.776 0.000193 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## 
## R-sq.(adj) =  0.204   Deviance explained = 21.9%
## GCV = 3199.2  Scale est. = 3125.7    n = 305
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model4-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Model required no smoothing parameter selectionModel rank =  7 / 7
\end{verbatim}

>>>>

  \title{Do larger catchments respond different to forest cover change?
Re-analysing a global data set.}
    \author[The University of Sydney, INIA]{R. Willem Vervoort\corref{1}}
   \ead{willem.vervoort@sydney.edu.au} 
    \author[INIA]{Eliana Nervi\corref{2}}
   \ead{eliananervi@gmail.com} 
    \author[IMFIA]{Jimena Alonso\corref{2}}
   \ead{jalonso@fing.edu.uy} 
      \address[The University of Sydney]{School of Life and Environmental Sciences, The University of Sydney,
Sydney, NSW 2006, Australia}
    \address[INIA]{INIA, Uruguay}
    \address[IMFIA]{Institute of Fluid Mechanics and Environmental Engineering, School of
Engineering, Universidad de la República, 11200 Montevideo, Departamento
de Montevideo, Uruguay}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

Several additional data points from watershed studies were extracted
from Zhang et al. (2011), Zhao et al. (2010), Borg et al. (1988),
Thornton et al. (2007), Zhou et al. (2010), Rodriguez et al. (2010),
Ruprecht et al. (1991) and Peña-Arancibia et al. (2012), and these were
checked against the existing studies to prevent overlap. In the citation
column in the data set, in general the main reference for the calculated
change in streamflow was used, because sometimes the original study did
not provide the quantification of the change in streamflow (i.e.~Table 6
in Zhang et al. (2011)). We also removed one data point from the
analysis, which corresponds to Watershed \#1 (Amazon) in Zhang et al.
(2017). This is because the cited reference (Roche, 1981) only relates
to 1 and 1.5 ha paired watershed studies in French Guyana, and in which
the actual change in forest cover is not recorded.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Zhang_all <-}\StringTok{ }\NormalTok{Zhang_all }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(}\StringTok{`}\DataTypeTok{Watershed #}\StringTok{`} \OperatorTok{>}\StringTok{ }\DecValTok{1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

Here \(X_i\) are factorial variables, while \(Z_i\) are continous
variables. The model assumes no direct interactions and all variables
are additive. The changes in forest cover contain both positive
(forestation) and negative values (deforestation). In Zhang et al.
(2017), these changes were jointly analysed, assuming the effect on the
change in flow was linear and non-hysteretic. However, the impact of an
increase in forest cover can be different from the same fractional
decrease in forest cover. Therefore all the change in forest cover data
is converted to positive values, and an additional column
(\emph{sign\_\{forest cover\}}) is added that indicates whether it was a
forest cover increase or decrease. A further assumption in the model is
that all continuous variables \(Z_i\) (such as annual precipitation
(Pa)) can have a linear or non-linear relationship with \(\Delta Q \%\).
This means that a smooth function \(s()\) is applied to the \(Z_i\)
variables.

@@

The overall dataset contains 311 observations of changes in flow. The
overall distribution of changes in flow is highly skewed as is the
distribution of changes in forest cover and Area. The values of changes
in flow greater than 100\% and smaller than -100\% clearly create long
tails on the change in flow distribution. Note also the large number of
studies with 100\% forest cover reduction. Smaller watersheds dominate
the database with 42\% of the data from watersheds \textless{} 1
km\textsuperscript{2} and 65\% of the data for watersheds \textless{} 10
km\textsuperscript{2}.

\begin{figure}
\includegraphics[width=0.9\linewidth]{DataExploration} \caption{Overview of the distributions of some of the variables in the data set}\label{fig:data_graphs}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\linewidth]{Increase_decrease} \caption{Changes in flow as a function of increases and decreases in forest cover}\label{fig:increase_decrease}
\end{figure}

This shows that for the data related to forest decreases, there is
almost always a positive flow change. In other words, flow almost always
increased. However, for increases in forest cover, this is not the case,
and flow can both increase and decrease. However in both cases the
variability in the reported change in flow increases with the increase
in forest cover change.

@@

\begin{longtable}[]{@{}ccccc@{}}
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
8.97\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
6.55\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
1.37\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.17\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.53\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.1\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
5.23\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-32.55\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
6.96\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-4.68\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}ccccc@{}}
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
23.27\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
9.21\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
2.53\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.01\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.54\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.1\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
5.2\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-33.29\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
6.99\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-4.77\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Area\_km2}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-0.16\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.87\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Pa\_mm}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-0.01\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-2.13\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.03\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}ccccc@{}}
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
35.23\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
10.31\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
3.42\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.51\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.1\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
4.92\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-38.06\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
7.26\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-5.24\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Area\_km2}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-0.46\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.64\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Pa\_mm}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-0.01\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.01\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-2.54\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.01\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Latitude}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-0.31\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.13\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-2.49\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.01\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Longitude}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-0.01\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.04\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-0.28\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.78\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

The previous analysis suggests an influence of radiation on
evapotranspiration, and most likely related to the dryness index, as
also indicated in Zhang et al. (2017). Increased evapotranspiration
could lead to drier catchments, unless balanced by rainfall (such as
possibly in the tropics). This model introduces the dryness index as a
linear variable and drops the annual average precipitation as a
variable.
